---
title: "Developing Data Products Week 2 Assignment"
author: "Joseph Michalski"
date: "8/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions

Create a web page using R Markdown that features a map created with Leaflet. 

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity! 

## My Submission

Using the below code, I created an interactive map of my local area.

```{r map}
library(leaflet)
library(dplyr)


map <- leaflet() %>%
  addTiles() %>%
  addMarkers(lat = 43.0389, lng = -87.9065, popup="Milwaukee, WI") %>%
  addMarkers(lat = 43.0117, lng = -88.2315, popup="Waukesha, WI") %>%
  addMarkers(lat = 43.0495, lng = -88.0076, popup="Wauwatosa, WI") %>%
  addMarkers(lat = 42.9764, lng = -88.1084, popup="New Berlin, WI") %>%
  addMarkers(lat = 43.0606, lng = -88.1065, popup="Brookfield, WI")
  
map
```